%-------------------------
% Resume in Latex
% Author : Raghav 
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Raghavendra S Navaratna} {\small (Raghav)} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:12179746100}{+1 (217) 974-6100}
    $|$
    \faAt \hspace{.5pt} \href{mailto:rsnavaratna@gmail.com}{rsnavaratna@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedIn.com/in/rsnavaratna}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/raghavvs}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://raghavvs.github.io}{Website}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Champaign,+IL/@40.1146258,-88.3121289,13z/data=!3m1!4b1!4m5!3m4!1s0x880cd08dde97691b:0x30f57847b475bfcf!8m2!3d40.1164204!4d-88.2433829?hl=en&authuser=0}{Champaign, USA}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {University of Illinois Urbana-Champaign (UIUC)}{Champaign, USA}
      {M.Sc. in  Aerospace Engineering;   \textbf{GPA: 3.77/10}}{Aug 2022 \textbf{--} Dec 2023 (Expected)}
      {Specialization: Control Systems and Dynamics  \textbf{ }}{ \textbf{} }
    
    \resumeSubheading
      {Dayananda Sagar College of Engineering (DSCE)}{Bangalore, India}
      {B.E. in  Mechanical Engineering;   \textbf{GPA: 8.61/10.00}}{Aug 2017 \textbf{--} May 2021}
    
  \resumeSubHeadingListEnd



%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {University of Illinois Urbana-Champaign}{Champaign, USA}
      {Independent Study $|$ \emph{\href{https://github.com/RMDLO/abb_dual_arm}{\textsl{\color{blue}GitHub}}}}{Sep 2022 \textbf{--} Current} 
        \resumeItemListStart
        	\resumeItem{Worked in the Robotics Lab with Dr.Timothy Bretl and Holly Dinkel on NASA funded project - "Astrobee Robot Challenge" - 						to build a dual-arm robotic system to detect and manipulate wires aboard the ISS.}
            \resumeItem{Updated the ROS drivers for the robotic arms to execute simultaneous and synchronous trajectory of two independent robotic 						arms.}
            \resumeItem{Worked on incorporating a secondary robotic arm into the ROS URDF file.}
            \resumeItem{Simulated the trajectory using MoveIt motion planning tool and validated by testing with physical arms.}
            \resumeItem{Built a framework for using industrial robots in multi-arm setup.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd



%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Indian Institute of Science}{Bangalore, India}
      {UAV Project Intern}{Jun 2021 \textbf{--} Sep 2021}
        \resumeItemListStart
            \resumeItem{Worked in the Department of Aerospace Engineering on design and development of unmanned aerial vehicles.}
            \resumeItem{Performance and stability analysis.}
            \resumeItem{Structural design and fabrication of amphibious UAV.}
            \resumeItem{Involved in CFRP and FRP manufacturing of flying wing UAV.}
        \resumeItemListEnd
    
    
  \resumeSubHeadingListEnd
  
  



%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{Autonomous Precision Landing of Model Rockets} $|$ (Bachelor's Thesis) $|$ \emph{\href{https://github.com/raghavvs/Autonomous-Landing-of-Model-Rockets}{\color{blue}GitHub}}}{} 
          \resumeItemListStart
            \resumeItem{Worked on detail design and development of rocket body and thrust vector control (TVC) system.}
            \resumeItem{Worked on aerodynamic, performance and stability analysis.}
            \resumeItem{Built a mathematical model to represent the dynamics of the rocket.}
            \resumeItem{Developed a PID and LQR-based controller to regulate attitude, altitude, and drift.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Balancing an Inverted Pendulum on a Cart} $|$ \emph{\href{https://github.com/raghavvs/Inverted-Pendulum-on-a-Cart}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Explored classical control approach to stabilize the inverted pendulum.}
            \resumeItem{Designed a Proportional Integral Derivative (PID) controller, a Linear Quadratic Regulator (LQR) for
						position and orientation control, and integrated a Kalman Filter for state estimation.}
			\resumeItem{Physical modeling of the inverted pendulum using Simscape.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Grid World problem using Reinforcement Learning} $|$ \emph{\href{https://github.com/raghavvs/Grid-world-reinforcement-learning}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{An archetype problem to learn and understand basics of reinforcement learning.}
            \resumeItem{Established Markov states and used dynamic programming - value iteration method.}
            \resumeItem{Implemented and solved the problem on python using OOP concepts.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Simulation of Kármán Vortex Street of Bluff Bodies for Piezoelectric Energy Harvesters} $|$ \emph{\href{https://github.com/raghavvs/Simulation-of-Karman-Vortex-Street-of-Bluff-Bodies-for-Piezoelectric-Energy-Harvesters}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Worked on the dynamics of coupled fluid-solid interaction, flow separation and boundary layer theory.}
            \resumeItem{Analyzed the effects of von Kármán vortex street on bluff bodies.}
            \resumeItem{Explored the possibilities of extracting energy from vortex induced vibrations on a piezoelectric material.}
          \resumeItemListEnd
      
      
    \resumeSubHeadingListEnd






%----------- Extracurricular Activites -----------

\section{Extracurricular Activites}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Team Arcis @DSCE}{Bangalore, India}
      {Team Manager}{Aug 2019 \textbf{--} Sep 2020}
        \resumeItemListStart
            \resumeItem{Primary responsibilities: planning, logistics, organizing and execution.}
            \resumeItem{Initiated participation of the team in AIAA – DBF.}
            \resumeItem{Worked on technical design report.}
            \resumeItem{Co-started a Research and Innovation Lab and co-built a subsonic wind tunnel.}
            \resumeItem{Participated in AIAA Design, Build, Fly, KANS, USA and SAE Aero Design West, CA, USA.}
        \resumeItemListEnd
        
     \resumeSubheading
      {Team Arcis @DSCE}{Bangalore, India}
      {Technical Engineer}{Aug 2017 \textbf{--} Jul 2019}
        \resumeItemListStart
            \resumeItem{Worked on technical presentation and technical design report.}
            \resumeItem{Design, fabrication and testing of unmanned aerial vehicles (UAVs).}
            \resumeItem{Worked on technical design report.}
            \resumeItem{Co-started a Research and Innovation Lab and co-built a subsonic wind tunnel.}
            \resumeItem{Participated in SAE Aero Design West, CA, USA and SAE Aero Design India.}
        \resumeItemListEnd
    
    
  \resumeSubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
    
        \textbf{Dayananda Sagar College of Engineering (DSCE): }{Best Project Award for - Bachelor’s thesis} \\ \vspace{3pt}
        
        \textbf{SAE Aero Design West: }{Secured $2^{nd}$ place in Micro Class in 2020} \\ \vspace{3pt}
        
        \textbf{SAE Aero Design West: }{Secured $1^{st}$ place in Technical Presentation in 2019} \\ \vspace{3pt}
          
    }}
  \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming:}{ C, C++, Python, MATLAB, XML, R} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ ROS, Simulink, Git, Arduino, Catia V5, Blender} \\ \vspace{3pt}
        
        \textbf{Languages:}{ Kannada (Native), English (Professional)}
    }}
  \resumeSubHeadingListEnd



%----------- MOOC -----------

\section{MOOCs}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Reinforcement Learning:}{ DeepMind} \\ \vspace{3pt}
        
        \textbf{Deep Learning Specialization:}{ deeplearning.ai} \\ \vspace{3pt}
        
        \textbf{Machine Learning:}{ Stanford University} \\ \vspace{3pt}
        
        \textbf{Fundamentals of Fluid-Solid Interaction: }{ École Polytechnique} \\ \vspace{3pt}
        
        \textbf{Design of Fixed Wing Unmanned Aerial Vehicles:}{ IIT Kanpur} 
    }}
  \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Business Skills, Data and Digital Skills, Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Swimming, Fitness, Eight-ball}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \resumeSubHeadingListStart
    
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}